Studies of quantum dots

### 2017-01-05 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex

The equations representing the DMC algorithm is obtained by applying the projection operator $\hat{P}(\tau)$ on the crude trial state $\ket{\Psi_T}$
\begin{equation}
 \hat{P}(\tau)\ket{\Psi_T} \equiv \exp\left({-(\hat{H} - E_0)\tau}\right)\ket{\Psi_T}
\end{equation}
\noindent
where $\tau$ is a constant often described as imaginary time, and $E_0=\bra{\Psi_0}\hat{H}\ket{\Psi_0}$ is the ground state of the Hamiltonian $\hat{H}$. By expanding the trial state in the eigenfunctions of $\hat{H}$, the ground state is obtained up to a constant factor

\begin{equation}
 \label{eq:DMC_ExactProjection}
 \lim_{\tau\to\infty} \bra{\mathbf{r}}  \hat{P}(\tau) \ket{\Psi_T} = \braket{\Psi_0}{\Psi_T}\Psi_0(\mathbf{r}).
\end{equation}

Defining $\Phi(\mathbf{r}, \tau) \equiv \bra{\mathbf{r}}\hat{P}(\tau)\ket{\Psi_T}$, we obtain the state at a later time $\tau + \delta\tau$ through projection

\begin{align}
 \Phi(\mathbf{r}, \tau + \delta\tau) &= \bra{\mathbf{r}} P(\tau + \delta\tau) \ket{\Psi_T} \notag\\
 &= \bra{\mathbf{r}} \exp\left({-(\hat{H} - E_0)\delta\tau}\right) \hat{P}(\tau) \ket{\Psi_T} \notag\\
 &= \bra{\mathbf{r}} \exp\left({-(\hat{H} - E_0)\delta\tau}\right) \ket{\Phi(\tau)} \notag\\
 &= \int \D\mathbf{r}' \bra{\mathbf{r}} \exp\left({-(\hat{H} - E_0)\delta\tau}\right)\ket{\mathbf{r}'} \Phi(\mathbf{r}', \tau)\notag \\
 &\equiv \int \D\mathbf{r}' G(\mathbf{r}, \mathbf{r}'; \delta\tau) \Phi(\mathbf{r}', \tau). \label{eq:DMC_GreenFuncRevealed}
\end{align}

@@

For evaluation of the local energy, the trial state is designed to cancel the Coulomb singularities by containing so-called correlation factors, however, this cancellation does not apply to the terms in the Green's function. In order to transfer this behavior to apply to the Green's function, a change to the formalism is introduced by iterating on a mixed density $f(\mathbf{r}, \tau) \equiv \Phi(\mathbf{r}, \tau)\Psi_T(\mathbf{r})$. Note that all previous arguments regarding convergence to the true ground state still applies for the new distribution.

Methods exist for transforming the mixed density into the pure density $|\Phi(\mathbf{r}, \tau)|^2$ \cite{abInitioMC}, but unless the pure density is explicitly needed (e.g.~for comparisons with other methods), this is strictly not necessary.

@@

\begin{align}
  G(\mathbf{r}, \mathbf{r}'; \delta\tau)_f &= \bra{\mathbf{r}} \exp\left({\frac{1}{2}\nabla\cdot \left[\left(\nabla - \mathbf{F}(\mathbf{r})\right)\right] - \left(E_L(\mathbf{r}) - E_T\right)}\right)\ket{\mathbf{r}'} \label{eq:DMC_IS_GF_raw}\\
  &\propto e^{-\left[|\mathbf{r} - \mathbf{r}' - \frac{1}{2}\delta\tau\mathbf{F}(\mathbf{r})|^2/2\delta\tau\right]} \label{eq:DMC_IS_GF}\\
  &\qquad\times e^{-\left[\frac{1}{2}\left[E_L(\mathbf{r'}) + E_L(\mathbf{r})\right] - E_T\right]\delta\tau} + \mathcal{O}(\delta\tau^2), \notag
\end{align}
where
\begin{equation}
  \mathbf{F}(\mathbf{r}) = 2\Psi_T(\mathbf{r})^{-1} \nabla \Psi_T(\mathbf{r})
\end{equation}

\noindent
is the drift vector commonly referred to as the \textit{quantum force}.

The local energy
\begin{equation}
E_L(\mathbf{r}) = \Psi_T(\mathbf{r})^{-1}\hat{H} \Psi_T(\mathbf{r})
\end{equation}
is necessarily sampled from $|\Psi_T(\mathbf{r})|^2$ (ensured by using the Metropolis Algorithm \cite{abInitioMC}) to avoid undefined energies when sampling close to the nodes of $\Psi_T(\mathbf{r})$.

@@

The name branching arise from the fact that in DMC, the weights are implemented as a probability of a given walker to copy or delete itself $n$ times, where $\langle n \rangle$ equals the branching term of \eqref{eq:DMC_IS_GF}. Let $G_b$ denote the value of the branching function at a given position. Correct weighting is then ensured by guaranteeing $m = \max\left(\mathrm{floor}\left(G_b\right)-1, 0\right)$ branches with a probability $G_b - m$ of getting an additional branch. A branch is an identical copy of the corresponding walker, with an identical past but with a different future. When the number of requested branches is zero, the walker is removed from the simulation.

Initially, $N_w$ walkers are initialized to span $|\Psi_T(\mathbf{r})|^2$. This is ensured by using the Metropolis Algorithm. Moreover, importance sampling is ensured by sampling according to the kinetic term of \eqref{eq:DMC_IS_GF_raw} [[cite solution langevin]]

\begin{equation}
x_{i+1} = x_i + \frac{1}{2}\delta\tau F(\mathbf{r})_x + \xi,
\end{equation}
\noindent
where $\xi$ is a uniform distributed random number with variance $\mathrm{Var}(\xi) = 2D\delta\tau$. A typical value of $N_w$ in this work is 250\,000.

For each time step, diffusion and branching repeats a given number of blocks $N_b$ for each walker. New branches are not active until the next time step, and if a walker hits zero branches the block repetition stops. During these block loops, the trial energy $E_T$ is sampled for use in the next time step $k+1$

\begin{equation}
 E_T^{k+1} = \frac{1}{M^{(k)}}\sum_{i=1}^{M^{(k)}} G_b(\mathbf{r}^{(k)}_i)E_L(\mathbf{r}^{(k)}_i),
\end{equation}
\noindent
where $M^{(k)}$ is the total number of samples obtained in cycle $k$. For this work we have found a value of $N_b = 100$ to be sufficient.

Several methods for estimating $E_0$ exist in the literature, one of which is simply an average of all $N_c$ trial energies calculated after $N_t$ thermalization cycles
\begin{equation}
 E_0 = \frac{1}{N_c-N_t}\sum\limits_{k=N_t}^{N_c} E_T^{(k)}.
\end{equation}
This is the relation we use in this work to obtain the DMC energies.

In this work, the trial state has been chosen to consist of a single Slater determinant (cite)
together with a single variational parameter Padé-Jastrow correlation function (cite).

The Slater determinant contains eigenstates $\phi_n(\mathbf{r})$ of the 2-dimensional harmonic oscillator
with a variational parameter $\alpha$ scaling the oscillator frequency $\omega$
such that $\omega\to\alpha\omega$ in all solutions:

\begin{equation}
 \phi_n(\mathbf{r}) = H_n(\sqrt{\alpha\omega}x)H_n(\sqrt{\alpha\omega}y)\exp(-\alpha\omega r^2),
\end{equation}

\noindent
where $H_n$ is the $n$'th level Hermite polynomial.

The eigenstates are selected such that the $N$ lowest lying energy eigenstates are selected (counting spin-degeneracy). Due to the Hamiltonian being spin independent we may split the Slater determinant into two equal parts -
one for each spin level (cite). The overall form of the trial state is as follows:

\begin{equation}
 \Psi_T(\mathbf{r}) = S(\mathbf{r}^\uparrow) S(\mathbf{r}^\downarrow) \prod_{i<j}^{N} J(r_{ij}),
\end{equation}

with

\begin{equation}
 S(\mathbf{r}^s) =  \left| \begin{array}{cccc}
\phi_1(\mathbf{r}^s_1) & \phi_2(\mathbf{r}^s_1)& \cdots & \phi_\frac{N}{2}(\mathbf{r}^s_1) \\
\phi_1(\mathbf{r}^s_2) & \phi_2(\mathbf{r}^s_2)& \cdots & \phi_\frac{N}{2}(\mathbf{r}^s_2) \\
\vdots & \vdots& \ddots & \vdots \\
\phi_1(\mathbf{r}^s_\frac{N}{2}) & \phi_2(\mathbf{r}^s_\frac{N}{2})& \cdots & \phi_\frac{N}{2}(\mathbf{r}^s_\frac{N}{2}) \\
 \end{array} \right|,
\end{equation}

and

\begin{equation}
 J(r_{ij}) = \exp\left(\frac{r_{ij}}{1 + \beta r_{ij}}\right),
\end{equation}

where $\mathbf{r}^s_i$ denotes $i$'th particle with spin $s$, and $r_{ij}$ is the relative distance between two electrons.
Since Metropolis Monte-Carlo only involves ratios of density functions, all normalization factors are skipped.

As a consequence of the variational principle, the optimal numeric values for $\alpha$ and $\beta$ can be found by minimizing the energy in the variational parameter space.
For this we have used the adaptive step gradient descent method (cite ASGD).

@@

A single Slater determinant and a simple correlation function opens up numerous optimization schemes which trivializes the CPU-time of most calculations.
We refer to Refs (cite optimization techniques) for more information.
Moreover, the most costly part of evaluating the single-particle eigenstates, the exponentials, is independent of the quantum number $n$, and can thus be tabulated once
for the entire calculation. This holds for the gradient and Laplacian needed in the quantum force and local energy, respectively, since the exponential shape is
preserved under differentiation.

@@

In this section, we discuss the IM-SRG results for the ground-state energies of closed-shell systems . In subsection \ref{subsec:Wegner}, we start with the Wegner generator. Numerical instabilities in the integration process, as well as a rather slow convergence as function of the number of oscillator shells, motivate the use of a Hartree-Fock basis and the Coulomb interaction.  Since higher correlations still lead to stiff equation systems, we change in subsection \ref{subsec:White} to the White generator. In particular, we give an overview of the IM-SRG(2) ground state energies for closed-shell systems up to $N=42$ particles and compare with other \textit{ab initio} many-body methods.

@@

In Figure \ref{fig:gs} we show the calculated ground state energies from Hartree-Fock, second-order (M\o ller-Plesset) perturbation theory (MPPT), and IM-SRG.  The exact result from diffusion Monte Carlo (DMC) is also shown as a dashed line in systems where it is known \cite{PhysRevB.84.115302}.

@@

To investigate the drifts, we tested our methods against a modified form of the Coulomb interaction, parametrized by two lengths $\sigma_{\mathrm{A}}$ and $\sigma_{\mathrm{B}}$ that characterize the range of the interaction:
\begin{align}
  V_{\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}}}(r) \equiv \frac{(1 + c)^{1 - 1/c}}{c} \left(1 - \E^{-r^2 / (2 \sigma_{\mathrm{A}}^2)}\right) \E^{-r^2 / (2 \sigma_{\mathrm{B}}^2)} \frac{1}{r}
\end{align}
where $c \equiv \sqrt{\sigma_{\mathrm{B}} / \sigma_{\mathrm{A}}}$.  The coefficient is defined to ensure the peak of the envelope remains at unity.  By setting $\sigma_{\mathrm{A}} = 0$ and $\sigma_{\mathrm{B}} = \infty$ one recovers the original Coulomb interaction.  By increasing $\sigma_{\mathrm{A}}$ one can reduce the short-range part of the interaction, and analogously by increasing $\sigma_{\mathrm{B}}$ one can reduce the long-range part of the interaction.  For our numerical experiments we consider the following four combinations of $(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}})$: $(0, \infty)$, $(\frac{1}{2}, \infty)$, $(0, 4)$, $(\frac{1}{2}, 4)$.

@@

>>>>

The equations representing the DMC algorithm is obtained by applying the projection operator $\hat{P}(\tau)$ on the crude trial state $\ket{\Psi_{\mathrm{T}}}$
\begin{equation}
 \hat{P}(\tau)\ket{\Psi_{\mathrm{T}}} \equiv \E^{-(\hat{H} - E_0)\tau} \ket{\Psi_{\mathrm{T}}}
\end{equation}
where $\tau$ is a constant often described as imaginary time, and $E_0=\bra{\Psi_0}\hat{H}\ket{\Psi_0}$ is the ground state of the Hamiltonian $\hat{H}$. By expanding the trial state in the eigenfunctions of $\hat{H}$, the ground state is obtained up to a constant factor
\begin{equation}
 \label{eq:DMC_ExactProjection}
 \lim_{\tau\to\infty} \bra{\bm{r}}  \hat{P}(\tau) \ket{\Psi_{\mathrm{T}}} = \braket{\Psi_0}{\Psi_{\mathrm{T}}}\Psi_0(\bm{r}).
\end{equation}

Defining $\Phi(\bm{r}, \tau) \equiv \bra{\bm{r}}\hat{P}(\tau)\ket{\Psi_{\mathrm{T}}}$, we obtain the state at a later time $\tau + \delta\tau$ through projection
\begin{align}
 \Phi(\bm{r}, \tau + \delta\tau) &= \bra{\bm{r}} P(\tau + \delta\tau) \ket{\Psi_{\mathrm{T}}} \notag\\
 &= \bra{\bm{r}} \E^{-(\hat{H} - E_0)\delta\tau} \hat{P}(\tau) \ket{\Psi_{\mathrm{T}}} \notag\\
 &= \bra{\bm{r}} \E^{-(\hat{H} - E_0)\delta\tau} \ket{\Phi(\tau)} \notag\\
 &= \int \D\bm{r}' \bra{\bm{r}} \E^{-(\hat{H} - E_0)\delta\tau} \ket{\bm{r}'} \Phi(\bm{r}', \tau)\notag \\
 &\equiv \int \D\bm{r}' G(\bm{r}, \bm{r}'; \delta\tau) \Phi(\bm{r}', \tau). \label{eq:DMC_GreenFuncRevealed}
\end{align}
which defines the Green's function $G$.

@@

For evaluation of the local energy, the trial state is designed to cancel the Coulomb singularities by containing so-called correlation factors, however, this cancellation does not apply to the terms in the Green's function. In order to transfer this behavior to apply to the Green's function, a change to the formalism is introduced by iterating on a mixed density $f(\bm{r}, \tau) \equiv \Phi(\bm{r}, \tau)\Psi_{\mathrm{T}}(\bm{r})$. Note that all previous arguments regarding convergence to the true ground state still applies for the new distribution.

Methods exist for transforming the mixed density into the pure density $|\Phi(\bm{r}, \tau)|^2$ \cite{abInitioMC}, but unless the pure density is explicitly needed (e.g.~for comparisons with other methods), this is strictly not necessary.

@@

\begin{align}
  G(\bm{r}, \bm{r}'; \delta\tau)_f &= \bra{\bm{r}} \E^{\frac{1}{2} \hat{\bm{\nabla}} \cdot \left(\hat{\bm{\nabla}} - \bm{F}(\bm{r})\right) - \left(E_{\mathrm{L}}(\bm{r}) - E_{\mathrm{T}}\right)} \ket{\bm{r}'} \label{eq:DMC_IS_GF_raw}\\
  &\propto \E^{-\left(|\bm{r} - \bm{r}' - \frac{1}{2}\delta\tau\bm{F}(\bm{r})|^2/(2\delta\tau)\right)} \label{eq:DMC_IS_GF}\\
  &\qquad\times \E^{-\left(\frac{1}{2}\left(E_{\mathrm{L}}(\bm{r'}) + E_{\mathrm{L}}(\bm{r})\right) - E_{\mathrm{T}}\right) \delta\tau} + \mathcal{O}\bigl((\delta\tau)^2\bigr), \notag
\end{align}
where
\begin{equation}
  \bm{F}(\bm{r}) = \frac{2 \hat{\bm{\nabla}} \Psi_{\mathrm{T}}(\bm{r})}{\Psi_{\mathrm{T}}(\bm{r})}
\end{equation}
is the drift vector commonly referred to as the \textit{quantum force}.

The local energy
\begin{equation}
E_{\mathrm{L}}(\bm{r}) \equiv \frac{\hat{H} \Psi_{\mathrm{T}}(\bm{r})}{\Psi_{\mathrm{T}}(\bm{r})}
\end{equation}
is necessarily sampled from $|\Psi_{\mathrm{T}}(\bm{r})|^2$ (ensured by using the Metropolis Algorithm \cite{abInitioMC}) to avoid undefined energies when sampling close to the nodes of $\Psi_{\mathrm{T}}(\bm{r})$.

@@

The name branching arise from the fact that in DMC, the weights are implemented as a probability of a given walker to copy or delete itself $n$ times, where $\langle n \rangle$ equals the branching term of \eqref{eq:DMC_IS_GF}. Let $G_{\mathrm{b}}$ denote the value of the branching function at a given position. Correct weighting is then ensured by guaranteeing $m = \max\{0, \lfloor G_{\mathrm{b}} \rfloor - 1\}$ branches\footnote{$\lfloor x \rfloor$ denotes the floor of $x$, namely the largest integer $n$ such that $n \le x$.} with a probability $G_{\mathrm{b}} - m$ of getting an additional branch.  A branch is an identical copy of the corresponding walker, with an identical past but with a different future. When the number of requested branches is zero, the walker is removed from the simulation.

Initially, $N_{\mathrm{w}}$ walkers are initialized to span $|\Psi_{\mathrm{T}}(\bm{r})|^2$. This is ensured by using the Metropolis Algorithm. Moreover, importance sampling is ensured by sampling according to the kinetic term of \eqref{eq:DMC_IS_GF_raw} [[cite solution langevin]]

\begin{equation}
x_{i+1} = x_i + \frac{1}{2} \delta \tau F(\bm{r})_x + \xi,
\end{equation}
where $\xi$ is a uniform distributed random number with variance $\operatorname{Var}(\xi) = 2D\delta\tau$. A typical value of $N_{\mathrm{w}}$ in this work is \num{250000}.

For each time step, diffusion and branching repeats a given number of blocks $N_{\mathrm{b}}$ for each walker. New branches are not active until the next time step, and if a walker hits zero branches the block repetition stops. During these block loops, the trial energy $E_{\mathrm{T}}$ is sampled for use in the next time step $k+1$
\begin{equation}
 E_{\mathrm{T}}^{k+1} = \frac{1}{M_k}\sum_{i=1}^{M_k} G_{\mathrm{b}}(\bm{r}^{(k)}_i)E_{\mathrm{L}}(\bm{r}^{(k)}_i),
\end{equation}
where $M_k$ is the total number of samples obtained in cycle $k$. For this work we have found a value of $N_{\mathrm{b}} = 100$ to be sufficient.

Several methods for estimating $E_0$ exist in the literature, one of which is simply an average of all $N_{\mathrm{c}}$ trial energies calculated after $N_{\mathrm{t}}$ thermalization cycles
\begin{equation}
 E_0 = \frac{1}{N_{\mathrm{c}}-N_{\mathrm{t}}} \sum_{k=N_{\mathrm{t}}}^{N_{\mathrm{c}}} E_{\mathrm{T}}^{(k)}.
\end{equation}
This is the relation we use in this work to obtain the DMC energies.

In this work, the trial state has been chosen to consist of a single Slater determinant [[cite]] together with a single variational parameter Pad\'e-Jastrow correlation function [[cite]].

The Slater determinant contains eigenstates $\phi_n(\bm{r})$ of the 2-dimensional harmonic oscillator
with a variational parameter $\alpha$ scaling the oscillator frequency $\omega$
such that $\omega\to\alpha\omega$ in all solutions:
\begin{equation}
 \phi_n(\bm{r}) = H_n(\sqrt{\alpha\omega}x)H_n(\sqrt{\alpha\omega}y)\E^{-\alpha\omega r^2}.
\end{equation}
where $H_n$ is the $n$th level Hermite polynomial.

The eigenstates are selected such that the $N$ lowest lying energy eigenstates are selected (counting spin-degeneracy). Due to the Hamiltonian being spin independent we may split the Slater determinant into two equal parts -
one for each spin level [[cite]]. The overall form of the trial state is as follows:
\begin{equation}
 \Psi_{\mathrm{T}}(\bm{r}) \equiv S(\bm{r}^\uparrow) S(\bm{r}^\downarrow) \prod_{i<j}^{N} J(r_{i,j}),
\end{equation}
with
\begin{equation}
 S(\bm{r}^s) \equiv \begin{vmatrix}
\phi_1(\bm{r}^s_1) & \phi_2(\bm{r}^s_1)& \cdots & \phi_{N/2}(\bm{r}^s_1) \\
\phi_1(\bm{r}^s_2) & \phi_2(\bm{r}^s_2)& \cdots & \phi_{N/2}(\bm{r}^s_2) \\
\vdots & \vdots& \ddots & \vdots \\
\phi_1(\bm{r}^s_{N/2}) & \phi_2(\bm{r}^s_{N/2})& \cdots & \phi_{N/2}(\bm{r}^s_{N/2}) \\
 \end{vmatrix},
\end{equation}
and
\begin{equation}
 J(r_{i, j}) \equiv \exp\left(\frac{r_{i, j}}{1 + \beta r_{i, j}}\right),
\end{equation}
where $\bm{r}^s_i$ denotes $i$'th particle with spin $s$, and $r_{ij}$ is the relative distance between two electrons.
Since Metropolis Monte-Carlo only involves ratios of density functions, all normalization factors are skipped.

As a consequence of the variational principle, the optimal numeric values for $\alpha$ and $\beta$ can be found by minimizing the energy in the variational parameter space.  For this we have used the adaptive step gradient descent method [[cite ASGD]].

@@

A single Slater determinant and a simple correlation function opens up numerous optimization schemes which trivializes the computation time of most calculations.  We refer to Refs [[cite optimization techniques]] for more information.  Moreover, the most costly part of evaluating the single-particle eigenstates, the exponentials, is independent of the quantum number $n$, and can thus be tabulated once for the entire calculation. This holds for the gradient and Laplacian needed in the quantum force and local energy, respectively, since the exponential shape is preserved under differentiation.

@@

[[Sarah's discussions on ground state energy are absent :(]]
In this section, we discuss the IM-SRG results for the ground-state energies of closed-shell systems.  We start with the Wegner generator in subsection [[??]].  Numerical instabilities in the integration process, as well as a rather slow convergence as function of the number of oscillator shells, favors the use of a Hartree-Fock basis and the Coulomb interaction.  Since higher correlations still lead to stiff equation systems, we change in subsection [[??]] to the White generator. In particular, we give an overview of the IM-SRG(2) ground state energies for closed-shell systems up to $N=42$ particles and compare with other \textit{ab initio} many-body methods.

@@

\subsection{Extrapolation}

In Figure \ref{fig:gs} we display a selection of ground state energies calculated using the Hartree-Fock method, second-order (M\o ller-Plesset) perturbation theory (MPPT), and IM-SRG.  The exact result from diffusion Monte Carlo (DMC) is also shown as a dashed line \cite{PhysRevB.84.115302}.

@@

\subsection{Slow convergence}

When the tail part of the convergence plots are magnified about a factor of ten or so [[double-check this number]], we noticed that the addition and removal energies are still drifting somewhat [[quantify how much]], hinting that the convergence rate is probably not exponential.

To investigate the rate of convergence, we tested our methods against a modified form of the Coulomb interaction, parametrized by two lengths $\sigma_{\mathrm{A}}$ and $\sigma_{\mathrm{B}}$ that characterize the range of the interaction:
\begin{align}
  V_{\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}}}(r) \equiv \frac{(1 + c)^{1 - 1/c}}{c} \left(1 - \E^{-r^2 / (2 \sigma_{\mathrm{A}}^2)}\right) \E^{-r^2 / (2 \sigma_{\mathrm{B}}^2)} \frac{1}{r}
\end{align}
where $c \equiv \sqrt{\sigma_{\mathrm{B}} / \sigma_{\mathrm{A}}}$.  The coefficient is defined to ensure the peak of the envelope remains at unity.  By setting $\sigma_{\mathrm{A}} = 0$ and $\sigma_{\mathrm{B}} = \infty$ one recovers the original Coulomb interaction.  By increasing $\sigma_{\mathrm{A}}$ one can reduce the short-range part of the interaction, and analogously by increasing $\sigma_{\mathrm{B}}$ one can reduce the long-range part of the interaction.  For our numerical experiments we consider the following four combinations of $(\sigma_{\mathrm{A}}, \sigma_{\mathrm{B}})$: $(0, \infty)$, $(\frac{1}{2}, \infty)$, $(0, 4)$, $(\frac{1}{2}, 4)$.

@@

\subsection{Extrapolation}

As suggested by Kvaal in \cite{PhysRevB.80.045321}, the asymptotic convergence of the wave function can be approximately described by a power law model: [[assuming I understood his paper correctly]]
\begin{align*}
  \Delta E \propto K^{-\beta}
\end{align*}
where $\Delta E$ is the error in the energy, $K$ is the number of shells in the single-particle basis, and $\beta$ is some positive real exponent.  Essentially, the \textit{smoothness} of the exact wave function determines the rate of the convergence: the more times the exact wave function can be differentiated, the higher the exponent $\beta$.

It is difficult to ascertain what $\beta$ is \textit{a priori}, but based on Kvaal's results $\beta$ is expected to be below $5$ for quantum dot systems.  To determine this from our numerical calculations, we perform a curve using the following power-law model:
\begin{align} \label{eq:power_law_model}
  E = \alpha K^{-\beta} + \gamma
\end{align}
As with most nonlinear curve fits, it is often fairly sensitive to the initial parameters.  To extract the initial parameters, we first do a linear fit on the logarithm of the \emph{derivative} $\partial E / \partial K$ against the logarithm of $K$:
\begin{align*}
  \ln \left(\frac{\partial E}{\partial K}\right) = \ln(\alpha) - \beta \ln(K)
\end{align*}
The derivative is computed numerically using finite differences of adjacent data points.  This amplifies the noise but linear fits do have the advantage of being very reliable to fit, hence the results are useful as guesses for the more accurate power-law fit.  This does not give us a guess for the infinite-basis energy $\gamma$, but we can estimate it by solving \label{eq:power_law_model} given a single data point and the (estimated) model paramters $\alpha$ and $\beta$.
